{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-06 Paper/main.tex
Small correction for b-splines
Changes for additional runs for application

	As this equation references knots that are not defined by the original vector of knots, implementations of this algorithm typically repeat the knots at the boundaries of the interval, $\tau_0$ and $\tau_L$ an additional $m$ times. This padding of the knot vector then allows to calculate every object that is needed for the definition of the chosen basis.\\

@@

	\subsection{Approximation and Smoothing via Basis Truncation}
	As mentioned above, the realized curves can be expressed in terms of a chosen functional basis. For this expansion, it is technically possible to use a complete basis of $\mathbb{L}^2[0,1]$. In many cases this is not a desirable approach as the expansion with too many basis functions introduces high amounts of variance in pronounced local variations of the curves or can even led to the approximation of noise in the sample curves, which possibly interrupts the analysis. {\color{red} Therefore, methods such as acceleration penalties have to be employed to smooth the function.} On the other hand, important information on the curves could be missed by using a number of basis functions that is too small. In that sense, this discussion is subject to the Bias-Variance tradeoff. It challenges the researcher to seek a point at which they truncate the basis function to remove noise and, at the same time, not to introduce too much bias by maintaining significant fluctuations of the curves. The basis expansion with truncation is defined by
	\begin{equation}
		X(\omega_0) = x(t) = \sum_{j \in \mathcal{I}} A_j(\omega_0) \phi_j(t) = \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t) + \delta(t) \approx \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t)
	\end{equation}
	where $\delta(t)$ is the truncation error and $L \leq \max\limits_{j \in \mathcal{I}}(j)$ for all $L \in \mathcal{I}$. The number $L$ can be chosen subjectively, but also through applying a data-driven method like Cross-Validation, which aims to minimize the Mean Squared Error (MSE) or other criteria. The significance of this choice of truncation becomes more evident in {\color{green} Link estimation} and is the subject of the simulation study.

>>>>

	As this equation references knots that are not defined by the original vector of knots, implementations of this algorithm typically repeat the knots at the boundaries of the interval, $\tau_0$ and $\tau_L$ an additional $m$ times. This padding of the knot vector then allows to calculate every object that is needed for the definition of the basis over the original set of knots.\\

@@

	\subsection{Approximation and Smoothing via Basis Truncation}
	As mentioned above, the realized curves can be expressed in terms of a chosen functional basis. For this expansion, it is technically possible to use a complete basis of $\mathbb{L}^2[0,1]$. In many cases this is not a desirable approach as the expansion with too many basis functions introduces high amounts of variance in pronounced local variations of the curves or can even led to the approximation of noise in the sample curves, which possibly interrupts the analysis. {\color{red} Therefore, methods such as acceleration penalties have to be employed to smooth the function.} On the other hand, important information on the curves could be missed by using a number of basis functions that is too small. In that sense, this discussion is subject to the Bias-Variance tradeoff. It challenges the researcher to seek a point at which they truncate the basis function to remove noise and, at the same time, not to introduce too much bias by maintaining significant fluctuations of the curves. The basis expansion with truncation is defined by
	\begin{equation}
		X(\omega_0) = x(t) = \sum_{j \in \mathcal{I}} A_j(\omega_0) \phi_j(t) = \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t) + \delta(t) \approx \sum_{j = 1}^{L} A_j(\omega_0) \phi_j(t)
	\end{equation}
	where $\delta(t)$ is the truncation error and $L \leq \max\limits_{j \in \mathcal{I}}(j)$ for all $L \in \mathcal{I}$. The number $L$ can be chosen subjectively, but also through applying a data-driven method like Cross-Validation, which aims to minimize the Mean Squared Error (MSE) or other criteria. The influence of this truncation on the prediction accuracy of different estimates is the subject of the simulation study.
